A novel route to the spontaneous formation of porous crystals via viscoelastic phase separation

### 2016-06-13 presentation/talk_Roscoff.tex
Crystals outgrow liquids Dynamics: Bergeron > Ostwald

>>>>

\begin{frame}{Crystals outgrow liquid}
\vspace{\baselineskip}
\tikzsetnextfilename{crystal_fates}%
\begin{tikzpicture}
\begin{groupplot}[%
			group style={
				group name=g, group size=2 by 1,
				horizontal sep=4em,
				},
		width=0.5\linewidth,
		%height=0.5\linewidth,
	]
	\nextgroupplot[
		title={crystals},
		xlabel={$t/10^3\tau_B$}, ylabel=\#,
		xmin=0, xmax=13.0, ymin=0,
		no marks,
		legend style={cells={anchor=base west}},
		]
	\addplot table[x expr={\thisrowno{0}/2.3e3}]{/data/Documents/tex/svn/crystal-gel/data/fig3a_1.dat} node[left] at (rel axis cs:1,0.2) {size};
	\addplot table[x expr={\thisrowno{0}/2.3e3}]{/data/Documents/tex/svn/crystal-gel/data/fig3a_2.dat} node[left] at (rel axis cs:1,0.6) {number};
	%\legend{average size, average number};

	\nextgroupplot[
		title={cluster size distribution},
		xlabel={$s$}, ylabel=$R_g/\sigma$,
		xmode=log, ymode=log,
		ytick={0.5, 1, 2, 4}, yticklabels={$\frac{1}{2}$, 1, 2, 4},
		domain=1:5e2,
		]
	\addplot[only marks, red, thick, mark=*] file{/data/Documents/tex/svn/crystal-gel/data/fig3d_sqrt_1.dat};
	\addplot[black, ultra thick] {0.522*x^(1/3)} node[below left] at (axis cs:9e2,2.5) {$D=3$};
	\addplot[gray, ultra thick] {0.426*x^(1/2.53)} node[pos=0.08,below right] {$D=2.53$};
\end{groupplot}
\end{tikzpicture}
\begin{center}
\includegraphics[height=6.5\baselineskip]{pathsX.pdf}
\end{center}
\end{frame}

\begin{frame}{Dynamics: Bergeron > Ostwald}
\vspace{\baselineskip}
\includegraphics[width=\textwidth]{/data/Documents/tex/svn/crystal-gel/nature/fig4.pdf}
\end{frame}
